SST_patterns

### 2019-09-22 SST_patterns.Rmd
update

As a common date we will use a start date from 1992-01-31 and end date 17-01-31

>>>>

As a common date we will use a start date from 1992-01-31 and end date 16-12-31

Using the generalised linear hypotheses - Look at the difference in count of upwelling within the different datasets (in situ, CMC, OISST). Look at the difference in duration of upwelling between the thre datasets.

To determine wether or not the same upwlling patterns are present at different distances from the coastline

Offshore Upwelling:
Which pixels showed the highest upwelling counts
Which site showed the most intense upwelling
